EvoSwarm: An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-05-13 draft.tex
Correct images

In Table~\ref{tab:time} we can see that as expected, and in most cases, 
increasing the number of workers reduces the time
required for the execution of an instance, 
mainly when using the same parameters
(number of populations and number of workers), that is, performance
scales with the number of workers for a fixed problem and number of
sub-populations used. See Table~\ref{tab:speedup:test} for a statistical test 
on speedup, this explain further in the next section.

>>>>

In Table~\ref{tab:time} we can see that as expected, and in most cases, 
increasing the number of workers reduces the time
required for the execution of an instance, 
mainly when using the same parameters
(number of populations and number of workers), that is, performance
scales with the number of workers for a fixed problem and number of
sub-populations used. The exception is the case when using five populations;
the time does not decrease when progressing from four to eight workers.  
That is because most of the time, workers are waiting for a population 
to be available in the message queue.
